Procurements of the Canadian Government, Runaway Military Contracts

### 2024-12-02 paper/paper.qmd
fixed

df <- read_csv(here::here("data/analysis_data/cleaned_data.csv"))
aggregated_df <- read_csv(here::here("data/analysis_data/top_ten_suppliers.csv"))
model <- read_rds(here::here("models/gen_model.rds"))
mil_model <- read_rds(here::here("models/mil_model.rds"))

aView(df)
```

>>>>

df <- read_csv(here::here("data/analysis_data/cleaned_data.csv"))
aggregated_df <- read_csv(here::here("data/analysis_data/top_ten_suppliers.csv"))
model <- read_rds(here::here("models/gen_model.rds"))
mil_model <- read_rds(here::here("models/mil_model.rds"))
```
